### 2009-02-01 articles/2009/geoinformatics/article.tex
Added author details and some notes to 'who uses QGIS' section
git-svn-id: https://svn.osgeo.org/qgis/trunk@10087 c8812cc2-4d05-0410-92ff-de0c093fc19c

\subsection{Who uses QGIS}
QGIS is now widely used by professionals, government and local agencies,
universities and students, and amateurs alike, for a large variety of tasks,
from simply viewing raster and vector data (especially useful is the capability
to deal with PostGIS layers) to running complex and custom analyses through
GRASS modules. Often is used to replace or integrate proprietary software, and
several migrations have been accomplished or are underway, both in small and in
large companies and public administrations. Among the hundreds of people that
have attended courses on QGIS use, a common feeling is that the switch from
proprietary software is painless, because many tasks and menus are very similar,
and the interface is generally judged very intuitive. No doubt thanks to its
free and open source licence, it is also used in some of the poorest countries,
thus helping to reduce the world digital divide and bring more geoinformatic
knowledge where local conditions are more difficult.
Professional support is provided by several companies.

@@

Otto Dassau <dassau@nature-consult.de>
\\Gary Sherman <sherman@mrcc.com>
\\Tim Sutton <tim@linfiniti.com>
\\Marco Hugentobler <marco.hugentobler@karto.baug.ethz.ch>
\\Paolo Cavallini <cavallini@faunalia.it>

>>>>

\subsection{Who uses QGIS}
QGIS is now widely used by professionals, government and local agencies,
universities and students, and amateurs alike, for a large variety of tasks,
from simply viewing raster and vector data (especially useful is the capability
to deal with PostGIS layers) to running complex and custom analyses through
GRASS modules. Often QGIS is used to replace or integrate proprietary software, and
several migrations have been accomplished or are underway, both in small and in
large companies and public administrations. Among the hundreds of people that
have attended courses on QGIS use, a common feeling is that the switch from
proprietary software is painless, because many tasks and menus are very similar,
and the interface is generally judged very intuitive. No doubt thanks to its
free and open source licence, it is also used in some of the poorest countries,
thus helping to reduce the world digital divide and bring more geoinformatic
knowledge where local conditions are more difficult.

QGIS is also used by many software developers to produce new GIS enabled
applications. As a Free alternative to GIS toolkits such as ESRI ArcObjects,
QGIS provides a compelling option. Yet more developers are building custom
plugins to suit their own needs and are sharing them via plugin repositories.

One of the curious aspects of being a Free and Open Source project is that we 
have very little idea of exactly how many users we have. Since the software can 
be freely copied and passed around after it is downloaded it is difficult to 
judge useage numbers. With around 1550 registered users on our community map 
we can extrapolate a user base in excess of 15000 given a conservative 
estimate of a 1% sign up rate.

Professional support is provided by several companies.

@@

Otto Dassau <dassau@nature-consult.de>
\\Gary Sherman <sherman@mrcc.com>
\\Tim Sutton <tim@linfiniti.com>: Tim runs a consultancy business in Gauteng,
South africa where he provides commercial support and development services for
QGIS and other FOSS GIS software.
\\Marco Hugentobler <marco.hugentobler@karto.baug.ethz.ch>
\\Paolo Cavallini <cavallini@faunalia.it>
